Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
ei => early / li => late

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASSR setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}). In thsi context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions.

@@

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, texture windows or centroids are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

@@

For both MFCCs and scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

@@

Outcomes for the scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the logarithmic compression. \gl{une idée du pourquoi ?}

>>>>

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{early}) for the ASSR setting, and both an early and a late integration (\emph{late}) strategy for the ASC setting (see Section \ref{sec:eili}). In thsi context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions.

@@

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, texture windows or centroids are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

@@

For both MFCCs and scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{early}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

@@

Outcomes for the scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{early} without the logarithmic compression. \gl{une idée du pourquoi ?}
